Landings by Length for Georges Bank

### 2021-06-22 docs/GBLandingsByLength.Rmd
added proportional landings by sizeclass data file and table in rmd

```{r hydraformat, echo=T, eval= F}
  speciesList <- unique(expanded$species_itis)
  for (itis in speciesList) {
    hydra_format(expanded,mscatch::fleets,itis)
  }
```

>>>>

```{r hydraformat, echo=T, eval= F}
speciesList <- unique(expanded$species_itis)
finalTable <- NULL
for (itis in speciesList) {
  itisData <- hydra_format(expanded,mscatch::fleets,itis)
  finalTable <- rbind(finalTable,itisData)
}

write.csv(finalTable,here::here("data-raw","catchAtLengthProportions.csv"))
```

The resulting table for the species of interest over 5 size class intervals. totalBiomass is in metric tons.

```{r props, echo = T,eval=T}
readr::read_csv(here::here("data-raw","catchAtLengthProportions.csv"),col_types = readr::cols()) %>% 
  dplyr::mutate(across(dplyr::starts_with("sizeclass"),round,5)) %>% 
  dplyr::mutate(totalBiomass=round(totalBiomass)) %>%
  DT::datatable(.,rownames = FALSE, 
          options = list(pageLength = 10, 
                         order = list(list(0, 'asc'))
          ))

## Assign fleets definition to hydra fleets

The [fleet](https://noaa-edab.github.io/ms-keyrun/GBFleetDecisions.html) definitions are further aggregated to meet the needs of the Hydra model
